---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Biodiveristy-stability relationships across taxa

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/744036049.svg)](https://zenodo.org/doi/10.5281/zenodo.10526501)
<!-- badges: end -->

Here you find the code and data necessary to reproduce the analysis in the manuscript: **Cross-taxa analysis of long-term data reveals a positive biodiversity-stability relationship with taxon-specific mechanistic underpinning**


## Repository structure
```{r, echo= FALSE}
fs::dir_tree(path = ".", recurse = 0, all = F, regexp = ".lock", invert = T)

```
### Main folders
In `data` you find all the data necessary to run the analysis and compute the diversity and stability metrics.  
In `function` you find the functions created optmize the analysis workflow.  
In `script` you find the code for the analysis and figures.  
In `output` you find the output from models, figures and table. 

### R project
We used the [{renv} package](https://rstudio.github.io/renv/index.html) to a create reproducible environments for the analysis. 

By downloading the full repository, you are able to use the `.Rproj` file to have the same environment as used in the analysis. 

**R version 4.2.2**
