---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Biodiveristy-stability relationships across taxa

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/744036049.svg)](https://zenodo.org/doi/10.5281/zenodo.10526501)
<!-- badges: end -->

Here you find the code and data necessary to reproduce the analysis in the manuscript:  

**Rodrigues and Rissanen et al.** *Cross-taxa analysis of long-term data reveals a positive biodiversity-stability relationship with taxon-specific mechanistic underpinning*.

## How to use the repository

Download the repository or clone it using the git command:

`git clone https://github.com/avrodrigues/bbs_across_taxa.git`

### Setting the environment

We used the R version 4.2.2 and the [{renv} package](https://rstudio.github.io/renv/index.html) v0.17.3 to create a reproducible environment for the analysis. 

After download the repository, you should run the code `renv::restore()`. It will install all the packages needed with the same version we used to produce the code and the analysis. Since it has several packages to be installed, this should take some time to be concluded. 

## Repository structure
```{r, echo= FALSE}
fs::dir_tree(path = ".", recurse = 0, all = F, regexp = ".lock", invert = T)

```
### Main folders
In `data` you find all the data necessary to run the analysis and compute the diversity and stability metrics.  
In `function` you find the functions created optimize the analysis workflow.  
In `script` you find the code for the analysis and figures.  
In `output` you find the output from models, figures and table. 


